Names diffusion and social class

### 2023-06-05 text/paper.tex
Updates from Overleaf

% Added link to preamble
\input{preamble}
\addbibresource{}
\documentclass{article}

@@

>>>>

% Added link to preamble
\input{preamble}
\addbibresource{}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=13cm]{plot/new_names_year.png}
    \caption{Number of new names per year in Chile (1920-2022)}
    \label{}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=13cm]{plot/name_commune.png}
    \caption{top names per commune in Chile (1920-2022)}
    \label{}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=13cm]{plot/names_commune_network.png}
    \caption{top names per commune in Chile (1920-2022)}
    \label{}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=13cm]{plot/top_nombre_comuna1.png}
    \caption{top names per commune in Chile (1920-2022)}
    \label{}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=13cm]{plot/top_nombre_comuna2.png}
    \caption{top names per commune in Chile (1920-2022)}
    \label{}
\end{figure}
